\documentclass{article}
%\voffset=-.12\textheight
%\textheight=1.24\textheight
\include{macros}
\usepackage{url}
\usepackage{color}
\definecolor{dblackcolor}{rgb}{0.0,0.0,0.0}
\definecolor{dbluecolor}{rgb}{.01,.02,0.7}
\definecolor{dredcolor}{rgb}{0.6,0,0}
\definecolor{dgraycolor}{rgb}{0.30,0.3,0.30}
\usepackage{listings} 
\usepackage{hyperref} 
\lstdefinelanguage{Sage}[]{Python}
{morekeywords={True,False,sage,singular},
sensitive=true}
\lstset{frame=none,
          showtabs=False,
          showspaces=False,
          showstringspaces=False,
          commentstyle={\ttfamily\color{dredcolor}},
          keywordstyle={\ttfamily\color{dbluecolor}\bfseries},
          stringstyle ={\ttfamily\color{dgraycolor}\bfseries},
          language = Sage,
	  basicstyle={\scriptsize \ttfamily},
	  aboveskip=.3em,
	  belowskip=.1em
          }

\title{\dred{Math 581e, Fall 2012, Homework 2}}
\author{William Stein ({\tt wstein@uw.edu})}
\date{Due: Friday, October 12, 2012}

\begin{document}

\maketitle

{\color{dbluecolor}There are \ref{last} problems. Turn your solutions in Friday, October
5, 2012 in class.  You may work with other people and can find the
\LaTeX{} of this file at \url{http://wstein.org/edu/2012/ant/hw/}.
Reminder: I normally have office hours 1:00--2:30 on Wednesdays in Padelford
C423 (except my Oct 10 office hours will instead be on Oct 8!).}

\begin{enumerate}

\item  Let $k$ be any field.  Prove that the polynomial ring $k[t]$ is noetherian.  \hint{This problem is very easy
if you have been paying attention.}
\item Let $k$ be a field.  Let $L$ be a finite degree field extension
  of the field $k(t)$, i.e., $L$ is a function field.  An element
  $\alpha \in F$ is an algebraic integer if there is some nonzero monic
  polynomial $f(x) \in k(t)[x]$ with coefficients in $k[t]$ such that
  $f(\alpha)=0$.
\begin{enumerate}
 \item  Prove that $1/t$ is not an algebraic integer.
 \item What is the minimial polynomial of $\sqrt{t} + \sqrt{1+t}$?  (You may assume $\Char(k)\neq 2$ if you want.)
 \item Prove that the set of algebraic integers in $L$ is a ring. 
\end{enumerate}
\item Let $\alpha = \sqrt{2} + \sqrt[3]{3}$.     (Use any method to answer this question; even just asking a computer.)
\begin{enumerate}
\item What is the matrix of multiplication by $\alpha$ on the field $\Q(\sqrt{2}, \sqrt[3]{3})$ 
with respect to some choice of basis (give the basis you use)?
\item What is the trace of $\alpha$? the norm of $\alpha$?
\item What is the minimial polynomial of $\alpha$?  
\end{enumerate}

\item\label{last} Let $K$ be a number field and $\alpha \in K$.  Prove
  that the matrix (with respect to some basis) of multiplication by
  $\alpha$ is diagonalizable (over $\C$).


\end{enumerate}

\end{document}
