\documentclass{article}
%\voffset=-.12\textheight
%\textheight=1.24\textheight
\include{macros}
\usepackage{url}
\usepackage{color}
\definecolor{dblackcolor}{rgb}{0.0,0.0,0.0}
\definecolor{dbluecolor}{rgb}{.01,.02,0.7}
\definecolor{dredcolor}{rgb}{0.6,0,0}
\definecolor{dgraycolor}{rgb}{0.30,0.3,0.30}
\usepackage{listings} 
\usepackage{hyperref} 
\lstdefinelanguage{Sage}[]{Python}
{morekeywords={True,False,sage,singular},
sensitive=true}
\lstset{frame=none,
          showtabs=False,
          showspaces=False,
          showstringspaces=False,
          commentstyle={\ttfamily\color{dredcolor}},
          keywordstyle={\ttfamily\color{dbluecolor}\bfseries},
          stringstyle ={\ttfamily\color{dgraycolor}\bfseries},
          language = Sage,
	  basicstyle={\scriptsize \ttfamily},
	  aboveskip=.3em,
	  belowskip=.1em
          }

\title{\dred{Math 581e, Fall 2012, Homework 3}}
\author{William Stein ({\tt wstein@uw.edu})}
\date{Due: Friday, October 19, 2012}

\begin{document}

\maketitle

{\color{dbluecolor}There are \ref{last} problems. Turn your solutions
  in Friday, October 19, 2012 in class.  You may work with other
  people and can find the \LaTeX{} of this file at
  \url{http://wstein.org/edu/2012/ant/hw/}.  If you use Sage to solve
  a problem, include your code in your solution. I have office hours
  12:30--2:00 on Wednesdays in Padelford C423.  }

\begin{enumerate}


\item Consider the ring $R=\Z[\sqrt{-5}]$.
\begin{enumerate}
\item Prove that $R$ is a Dedekind domain.
\item Prove that the number $6$ factors
  in two completely different ways as a product of irreducible
  elements.  \hint{{\em Irreducible} means ``not a product of two
  non-units''.}
\item Explicitly factor $6R$ as a product of prime ideals. \hint{You can use Sage for this.}
\end{enumerate}

\item Let $\Zbar$ be the ring of all algebraic integers in
  a fixed choice of $\Qbar$.  Then $\Zbar$ is {\em not} a Dedekind
  domain.  Which of the three properties of a Dedekind domain does the
  ring $\Zbar$ satisfy (give proof)?  \hint{The properties are: (1) every nonzero prime is maximal,
  (2) noetherian, (3) integrally closed in its field of fractions.}

\item Use Sage to find a basis for the ring of integers of the number
  field obtained by adjoining one root of the polynomial $x^3 + x^2 -
  2x + 8$ to $\Q$.

\item\label{last} Let $K$ be a field of the form $\F_q(t)[x]/(g)$ with
  $\F_q$ a finite field and $g\neq 0$, so $K$ is obtained from
  $\F_q(t)$ by adjoining one algebraic element.  Let $\cO_K$ be the
  ring of elements of $K$ that satisfy a nonzero monic polynomial with
  coefficients in $\F_q[t]$.  Make the further assumption that $\cO_K$
  is finitely generated as an $\F_q[t]$ module.  Prove that every
  prime ideal of $\cO_K$ is maximal.

\end{enumerate}

\end{document}
