\documentclass{article}
%\voffset=-.12\textheight
%\textheight=1.24\textheight
\include{macros}
\usepackage{url}
\usepackage{color}
\definecolor{dblackcolor}{rgb}{0.0,0.0,0.0}
\definecolor{dbluecolor}{rgb}{.01,.02,0.7}
\definecolor{dredcolor}{rgb}{0.6,0,0}
\definecolor{dgraycolor}{rgb}{0.30,0.3,0.30}
\definecolor{dgreen}{rgb}{0,0.3,0}
\usepackage{listings} 
\usepackage{hyperref} 
\lstdefinelanguage{Sage}[]{Python}
{morekeywords={True,False,sage,singular},
sensitive=true}
\lstset{frame=none,
          showtabs=False,
          showspaces=False,
          showstringspaces=False,
          commentstyle={\ttfamily\color{dredcolor}},
          keywordstyle={\ttfamily\color{dbluecolor}\bfseries},
          stringstyle ={\ttfamily\color{dgraycolor}\bfseries},
          language = Sage,
	  basicstyle={\scriptsize \ttfamily},
	  aboveskip=.3em,
	  belowskip=.1em
          }

\title{\dred{Math 581e, Fall 2012, Homework 6}}
\author{William Stein ({\tt wstein@uw.edu})}
\date{Due: Friday, November 9, 2012}

\begin{document}

\maketitle

{\color{dbluecolor}There are \ref{last} problems. Turn your solutions
  in Friday, November 9, 2012 in class.  You may work with other
  people and can find the \LaTeX{} of this file at
  \url{http://wstein.org/edu/2012/ant/hw/}.  If you use Sage to solve
  a problem, include your code in your solution. I have office hours
  12:30--2:00 on Wednesdays in Padelford C423.  }

\begin{enumerate}

\item Explicitly determine the class group of $\Q(\sqrt{23})$ by
  computing the Minkowski bound, enumerating ideals, etc., like I did
  with $\Q(\sqrt{10})$ in class.  Show as many details as you can.
  Also, double check your answer by computing the class group in Sage
  and comparing results.

\item It is generally conjectured (and easy to be convinced from data)
  that there are infinitely many quadratic fields of class number 1,
  though nobody knows how to prove this. Do you think there are
  infinitely many {\em cubic} number fields of class number $1$?  Give
  computational evidence for your conjecture.

\item \label{last} Provide a status update on your final project
  (which is due {\bf December 7}).
\begin{enumerate}
\item What is the latest title/abstract?
\item How far along have you got with it?  (How many hours left until it is polished and done?)
\item Any questions for me about it?
\end{enumerate}

\end{enumerate}

\end{document}
